Penalized linear mixed models for structured genetic data

### 2021-02-25 main.tex
Most recent genome wide figures, full page dag pdfs to get turned into eps files
Updating Figures 5, 6 (empirical genome-wide analysis)

\begin{equation}
\centering
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
    \node (1) at (0,0) {Population Stratification};
    \node (2) [right = of 1] {Environment};
    \node (3) [below = of 1] {Observed SNPs};
    \node (4) [below = of 2] {Phenotype};
    \path[bidirected, -] (1) edge (2);
    \path[line width = 0.5] (1) edge (3);
    \path (2) edge (4);
    \path (3) edge (4);
    \tkzMarkSegment[pos=.5,mark=x](1,3)
\end{tikzpicture}
%\caption{The causal pathway between the environment and observed SNPs may be indirectly blocked by many methods that attempt to reduce confounding due to population structure.}
\label{diag:ps_env_block}
\end{equation}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/beta_mse.png}
    \caption{Estimation accuracy of different methods for different data types in the presence and absence of environmental confounding with 4 subpopulations. Mean and 1 SE bars displayed for 1000 replications.}
    \label{fig:mse}
\end{figure}

@@

>>>>

\begin{equation}
\centering
\begin{tikzpicture}[baseline=(current  bounding  box.center)]
    \node (1) at (0,0) {Population Stratification};
    \node (2) [right = of 1] {Environment};
    \node (3) [below = of 1] {Observed SNPs};
    \node (4) [below = of 2] {Phenotype};
    \path[bidirected, -] (1) edge (2);
    \path[line width = 0.5] (1) edge (3);
    \path (2) edge (4);
    \path (3) edge (4);
    \tkzMarkSegment[pos=.5,mark=x](1,3)
\end{tikzpicture}
\label{diag:ps_env_block}
\end{equation}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/beta_mse.png}
    \caption{Estimation accuracy of different methods for different data types in the presence and absence of environmental confounding with 4 subpopulations. Mean and 1 standard error (SE) bars displayed for 1000 replications.}
    \label{fig:mse}
\end{figure}

@@

%------------------------------%
\subsection{\anna{Genome-wide analysis case study}}
%------------------------------%

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\caption{Precision recall curves across $\lambda$ values from the Empirical genome-wide analysis. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pc1_corr.png}
\caption{Pathwise absolute correlation of selected, non-causal SNPs with the first principal component of the data in Empirical genome-wide analysis. Plotted line is the mean absolute correlation of all incorrectly selected SNPs for a particular $\lambda$ value, with shaded region for $\pm$ 1 SE. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_pc1_corr}
\end{figure}
